---
title: "Figure 3H: TetONC661S Cells / Calnexin"
author: "Sandra Vidak/Gianluca Pegoraro"
date: "October 27th 2022"
output: github_document
---

### Introduction

Columbus screen names:

`180124-40x-TetON-d50C661S-1868-GRP94-HSF1-SUN1-ctrl_20180124_122631`

`20191017-40x-TetON-C661S10-GRP94-Hsc70-Hsp40_20191017_132153`

`220803-40x-bin2-TetONC661S-Calnexin_20220803_120715`

### Analysis Setup

Load required packages.

```{r load-packages}
library(tidyverse)
library(fs)
library(Hmisc)
library(ggthemes)
library(DescTools) # for Dunnett's Test
source("R/Plotters.R") #Functions needed for plotting
```

```{r set-knitr-options, include=FALSE}
knitr::opts_chunk$set(
  fig.path = 'output/',
  message = FALSE,
  warning = FALSE
  )
```

Set the palette and the running theme for ggplot2.

```{r set-theme-palette,include=FALSE}
theme_set(theme_bw())
theme_update(axis.text.x = element_text(
angle = -45,
hjust = 0,
vjust = 0.5
))
```

### Experimental Metadata

Read plate layouts.

```{r read-metadata}
cell_levs <- c("Uninduced", "Induced")

plate_layouts <- read_tsv("metadata/plate_layout.txt") %>%
  filter(!is.na(cell_line)) %>%
  separate(col = cell_line, 
           into = c("cell_line"), 
           remove = T) %>%
  mutate(cell_line = factor(cell_line, levels = cell_levs))

glimpse(plate_layouts)
```

Plot plate layouts.

```{r cell-line-layout, echo=FALSE}
plot_plate(
  plate_layouts,
  property = cell_line,
  discrete_property = T,
  legend = "Cell Line",
  title = "Cell Lines Layout"
)
```

```{r ab-layout, echo=FALSE}
plot_plate(
  plate_layouts,
  property = marker,
  discrete_property = T,
  legend = "IF Antibody Layout",
  title = "Primary Ab"
)
```

### Read and Process Columbus data

Recursively search the `input` directory and its subdirectories for files whose name includes the Glob patterns defined in the chunk above, and read the cell-level Columbus data from the results text files.

```{r read-columbus-data, message=FALSE}
read_columbus_results <- function(path, glob) {
  dir_ls(path = path,
         recurse = T,
         glob = glob)  %>%
    read_tsv(
      id = "file_name"
    ) %>%
    select(
      screen = ScreenName,
      plate = PlateName,
      well = WellName,
      row = Row,
      column = Column,
      nuc_area = `Nuclei Selected - Nucleus Area [px²]`,
      cyto_area = `Nuclei Selected - Cytoplasm Area [px²]`,
      cell_area = `Nuclei Selected - Cell Area [px²]`,
      nuc_marker_int = `Nuclei Selected - Intensity Nucleus BP600/37 Mean`,
      cyto_marker_int = `Nuclei Selected - Intensity Cytoplasm BP600/37 Mean`,
      ratio_marker_int = `Nuclei Selected - Nuc_Cyto_BP600_Ratio`
    )
}

glob_path <- "*- Nuclei Selected[0].txt"
col_tbl <- read_columbus_results("input", glob_path)

glimpse(col_tbl)
```

Join Columbus data with the plate layout information.

```{r merge-metadata}
cell_tbl <- col_tbl %>%
  mutate(sum_marker_int = nuc_marker_int + cyto_marker_int) %>%
  inner_join(plate_layouts,
             by = c("row", "column","screen")) %>%
  select(screen,
         plate,
         well,
         row,
         column,
         cell_line,
         marker,
         nuc_area:sum_marker_int)

glimpse(cell_tbl)
```

Calculate number of cells and mean per well for all properties.

```{r well-summarise}
well_tbl <- cell_tbl %>%
  group_by(screen,
           well,
           row,
           column,
           cell_line,
           marker) %>%
  summarise(cell_n = n(),
            across(nuc_area:sum_marker_int,
                   list(mean = ~ mean(.x, na.rm = T))))

glimpse(well_tbl)
```

Calculate the mean of the technical replicates for each biological replicate. Now every marker/cell line combination has an n = 3 biological replicates.

```{r bioreps-summarise}
bioreps_tbl <- well_tbl %>%
  group_by(screen,
           cell_line,
           marker) %>%
  summarise(across(cell_n:sum_marker_int_mean,
                    ~ mean(.x, na.rm = T)))

glimpse(bioreps_tbl)
```

### Biological Replicates Level plot for Fig.3H

```{r Fig3_H, fig.width=4,fig.height=4.5, echo = FALSE}
bioreps_tbl %>%
  plot_crossbars(property = sum_marker_int_mean,
                 property_legend = "Total Mean Intensity (A.U), +/- SD",
                 title = "Per Well Total Intensity")
```

### Calculate Dunnett's test for the continuous variables.

Define a custom function to run a Dunnett post-hoc test only on the Mean marker intensity sum (Cyto + Nucleus), using the cell line as the predictor variable, and fixing Uninduced as the negative control. The output of the Dunnett's test is then rearranged to a tidy table to make it work with `dplyr`.

```{r}
calc_dunnett <- function(df){
  as.data.frame(as.table(DunnettTest(ratio_marker_int_mean ~ cell_line,
                          control = "Uninduced",
                          data = df)$Uninduced)) %>%
    pivot_wider(names_from = Var2, values_from = Freq) %>%
    rename(comparison = Var1)
}
```

Run the custom function on all the data grouped based on the IF marker and save the data to a .csv file.

```{r results='asis'}
dunnett_test <- bioreps_tbl %>%
  group_by(marker) %>%
  group_modify(~ calc_dunnett(.x))

write_csv(dunnett_test, "output/dunnett_results.csv")

knitr::kable(dunnett_test, digits = 3)
```

Document the information about the analysis session

```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```
