---
title: "Figure 3C and 3D: TETON Cells / GRP78"
author: "Sandra Vidak"
date: "November 16th 2022"
output: github_document
---

```{r load-packages}
library(ggplot2)
library(ggthemes)
library(curl)
```

```{r set-knitr-options, include=FALSE}
knitr::opts_chunk$set(
  fig.path = 'output/',
  message = FALSE,
  warning = FALSE
  )
```

### Download the data if needed

Download and unzip the Columbus results of the experiments from Figshare if they have not been already downloaded.

```{r download-data}
if(!dir.exists("input")) {
  URL <- "https://figshare.com/ndownloader/files/38158203"
  curl_download(URL, "input.zip")
  unzip("input.zip")
}
```

### Read Data for Fig 3C

Import and filter data and calculate sum and mean of the GRP78 peripheral recruitment for each biological replicate in TetON fibroblasts.

```{r}
GRP78_ring_1 <- read.csv(file="input/GRP78ring1.csv")

GRP78_ring_1_filtered <- GRP78_ring_1 [ c(seq(1, nrow(GRP78_ring_1),3)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_1_filtered_rowsum <- rowSums(GRP78_ring_1_filtered[,1:2])


Mean_Uninduced_GRP78_1 <- mean(GRP78_ring_1_filtered_rowsum[1:3])

Mean_Induced_4days_GRP78_1 <- mean(GRP78_ring_1_filtered_rowsum[7:9])

```

```{r}
GRP78_ring_2 <- read.csv(file="input/GRP78ring2.csv") 

GRP78_ring_2_filtered <- GRP78_ring_2 [ c(seq(1, nrow(GRP78_ring_2),10)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_2_filtered_rowsum <- rowSums(GRP78_ring_2_filtered[,1:2])


Mean_Uninduced_GRP78_2 <- mean(GRP78_ring_2_filtered_rowsum[1:3])

Mean_Induced_4days_GRP78_2 <- mean(GRP78_ring_2_filtered_rowsum[7:9])
```

```{r}
GRP78_ring_3 <- read.csv(file="input/GRP78ring3.csv") 

GRP78_ring_3_filtered <- GRP78_ring_3 [ c(seq(1, nrow(GRP78_ring_3),8)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_3_filtered_rowsum <- rowSums(GRP78_ring_3_filtered[,1:2])


Mean_Uninduced_GRP78_3 <- mean(GRP78_ring_3_filtered_rowsum[1:3])

Mean_Induced_4days_GRP78_3 <- mean(GRP78_ring_3_filtered_rowsum[7:9])
```

```{r}
GRP78_Uninduced <- c(Mean_Uninduced_GRP78_1, Mean_Uninduced_GRP78_2, Mean_Uninduced_GRP78_3)

GRP78_Induced4days <- c(Mean_Induced_4days_GRP78_1, Mean_Induced_4days_GRP78_2, Mean_Induced_4days_GRP78_3)


GRP78_df <- data.frame (GRP78_Uninduced,GRP78_Induced4days)

rownames(GRP78_df) <- c("Biological replicate1", "Biological replicate2", "Biological replicate3")

GRP78_df
```

Calculate mean and SD for 3 different biological replicates in every condition

```{r}
Mean_GRP78_levels <- apply(GRP78_df,2,mean)

SD_GRP78_levels <- apply(GRP78_df,2,sd)

Mean_GRP78_levels2 <- as.data.frame(Mean_GRP78_levels)

SD_GRP78_levels2 <- as.data.frame(SD_GRP78_levels)
Condition <- rep(c("GFP-progerin OFF","GFP-progerin ON"), each=1)
GRP78_plot <- data.frame(Mean_GRP78_levels2,SD_GRP78_levels2, Condition)
```

### Biological Replicates Level plot for Fig.3C

```{r Fig_3C, echo=FALSE}
ggplot(GRP78_plot, aes(x = Condition, 
                       y = Mean_GRP78_levels, 
                       ymin = Mean_GRP78_levels-SD_GRP78_levels, 
                       ymax = Mean_GRP78_levels+SD_GRP78_levels)) +
  geom_crossbar()+ 
  ylab("Mean Peripheral Intensity +/-SD [a.u.]") + 
  ggtitle("Per Well Total Intensity") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,15000))
```

### Read and Process Data for Fig 3D

Import and filter data and calculate sum and mean of the GRP78 peripheral recruitment for each biological replicate in h-Tert immortalized patient fibroblasts

```{r}
GRP78_ring_1 <- read.csv(file="input/GRP78ring1_1.csv") 
GRP78_ring_WT_1_filtered <- GRP78_ring_1 [ c(seq(13, nrow(GRP78_ring_1),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_WT_1_filtered_rowsum <- rowSums(GRP78_ring_WT_1_filtered[,1:2])


GRP78_ring_HGPS1_1_filtered <- GRP78_ring_1 [ c(seq(15, nrow(GRP78_ring_1),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_HGPS1_1_filtered_rowsum <- rowSums(GRP78_ring_HGPS1_1_filtered[,1:2])

GRP78_ring_HGPS2_1_filtered <- GRP78_ring_1 [ c(seq(16, nrow(GRP78_ring_1),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_HGPS2_1_filtered_rowsum <- rowSums(GRP78_ring_HGPS2_1_filtered[,1:2])


Mean_WT_1 <- mean(GRP78_ring_WT_1_filtered_rowsum[1:3])

Mean_HGPS1_1 <- mean(GRP78_ring_HGPS1_1_filtered_rowsum[1:3])

Mean_HGPS2_1 <- mean(GRP78_ring_HGPS2_1_filtered_rowsum[1:3])
```

```{r}
GRP78_ring_2 <- read.csv(file="input/GRP78ring2_1.csv") 

GRP78_ring_WT_2_filtered <- GRP78_ring_2 [ c(seq(1, nrow(GRP78_ring_2),16)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_WT_2_filtered_rowsum <- rowSums(GRP78_ring_WT_2_filtered[,1:2])


GRP78_ring_HGPS1_2_filtered <- GRP78_ring_2 [ c(seq(9, nrow(GRP78_ring_2),16)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_HGPS1_2_filtered_rowsum <- rowSums(GRP78_ring_HGPS1_2_filtered[,1:2])


GRP78_ring_HGPS2_2_filtered <- GRP78_ring_2 [ c(seq(13, nrow(GRP78_ring_2),16)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_HGPS2_2_filtered_rowsum <- rowSums(GRP78_ring_HGPS2_2_filtered[,1:2])


Mean_WT_2 <- mean(GRP78_ring_WT_2_filtered_rowsum[1:3])

Mean_HGPS1_2 <- mean(GRP78_ring_HGPS1_2_filtered_rowsum[1:3])

Mean_HGPS2_2 <- mean(GRP78_ring_HGPS2_2_filtered_rowsum[1:3])
```

```{r}
GRP78_ring_3 <- read.csv(file="input/GRP78ring3_1.csv") 

GRP78_ring_WT_3_filtered <- GRP78_ring_3 [ c(seq(1, nrow(GRP78_ring_3),16)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]


GRP78_ring_WT_3_filtered_rowsum <- rowSums(GRP78_ring_WT_3_filtered[,1:2])

GRP78_ring_HGPS1_3_filtered <- GRP78_ring_3 [ c(seq(9, nrow(GRP78_ring_3),16)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_HGPS1_3_filtered_rowsum <- rowSums(GRP78_ring_HGPS1_3_filtered[,1:2])

GRP78_ring_HGPS2_3_filtered <- GRP78_ring_3 [ c(seq(13, nrow(GRP78_ring_3),16)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_ring_HGPS2_3_filtered_rowsum <- rowSums(GRP78_ring_HGPS2_3_filtered[,1:2])


Mean_WT_3 <- mean(GRP78_ring_WT_3_filtered_rowsum[1:3])

Mean_HGPS1_3 <- mean(GRP78_ring_HGPS1_3_filtered_rowsum[1:3])

Mean_HGPS2_3 <- mean(GRP78_ring_HGPS2_3_filtered_rowsum[1:3])
```

```{r}
GRP78_WT <- c(Mean_WT_1, Mean_WT_2, Mean_WT_3)

GRP78_HGPS1 <- c(Mean_HGPS1_1, Mean_HGPS1_2, Mean_HGPS1_3)

GRP78_HGPS2 <- c(Mean_HGPS2_1, Mean_HGPS2_2, Mean_HGPS2_3)


GRP78_df <- data.frame (GRP78_WT,GRP78_HGPS1,GRP78_HGPS2)
rownames(GRP78_df) <- c("Biological replicate1", "Biological replicate2", "Biological replicate3")

GRP78_df
```

Calculate mean and SD for 3 different biological replicates in every condition

```{r}
Mean_GRP78_levels <- apply(GRP78_df,2,mean)

SD_GRP78_levels <- apply(GRP78_df,2,sd)

Mean_GRP78_levels2 <- as.data.frame(Mean_GRP78_levels)

SD_GRP78_levels2 <- as.data.frame(SD_GRP78_levels)
Condition <- rep(c("WT","HGPS1", "HGPS2"), each=1)

GRP78_plot <- data.frame(Mean_GRP78_levels2,SD_GRP78_levels2, Condition)
```

### Biological Replicates Level plot for Fig.3D

```{r Fig_3D, echo=FALSE}
ggplot(GRP78_plot, 
       aes(x = reorder(Condition,Mean_GRP78_levels), 
           y = Mean_GRP78_levels, 
           ymin = Mean_GRP78_levels-SD_GRP78_levels, 
           ymax = Mean_GRP78_levels+SD_GRP78_levels)) +
  geom_crossbar()+ 
  ylab("Mean Peripheral Intensity +/-SD [a.u.]") + 
  ggtitle("Per Well Total Intensity")  + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,8000))
```

Document the information about the analysis session

```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```
