---
title: "Figure S1H and S2A: hTERT-Progeria / Calnexin"
author: "Sandra Vidak/Gianluca Pegoraro"
date: "March 13th 2023"
output: github_document
---

### Introduction

Columbus screen names:

`180124-40x-hFibro-Calnexin-Hsp40_20180124_111314`

`180129-40x-hFibro-Calnexin-HSF1_20180129_130358`

`180205-40x-hFibro-Calnexin-Hsp70-Hsp90-SUN1_20180205_112614`

### Analysis Setup

Load required packages.

```{r load-packages}
library(tidyverse)
library(fs)
library(Hmisc)
library(ggthemes)
library(DescTools) # for Dunnett's Test
library(curl)
source("R/Plotters.R") #Functions needed for plotting
```

```{r set-knitr-options, include=FALSE}
knitr::opts_chunk$set(
  fig.path = 'output/',
  message = FALSE,
  warning = FALSE
  )
```

Set the palette and the running theme for ggplot2.

```{r set-theme-palette,include=FALSE}
theme_set(theme_bw())
theme_update(axis.text.x = element_text(
angle = -45,
hjust = 0,
vjust = 0.5
))
```

### Experimental Metadata

Read plate layouts.

```{r read-metadata}
cell_levs <- c("WT", 
               "HGPS1","HGPS2")

plate_layouts <- read_tsv("metadata/plate_layout.txt") %>%
  filter(!is.na(cell_line)) %>%
  separate(col = cell_line, 
           into = c("cell_line", "cell_id"), 
           remove = T) %>%
  mutate(cell_line = factor(cell_line, levels = cell_levs))

glimpse(plate_layouts)
```

Plot plate layouts.

```{r cell-line-layout, echo=FALSE}
plot_plate(
  plate_layouts,
  property = cell_line,
  discrete_property = T,
  legend = "Cell Line",
  title = "Cell Lines Layout"
)
```

```{r ab-layout, echo=FALSE}
plot_plate(
  plate_layouts,
  property = marker,
  discrete_property = T,
  legend = "IF Antibody Layout",
  title = "Primary Ab"
)
```

### Download the data if needed

Download and unzip the Columbus results of the experiments from Figshare if they have not been already downloaded.

```{r download-data}
if(!dir.exists("input")) {
  URL <- "https://figshare.com/ndownloader/files/38669186"
  curl_download(URL, "input.zip")
  unzip("input.zip")
}
```

### Read and Process Columbus data

Recursively search the `input` directory and its subdirectories for files whose name includes the Glob patterns defined in the chunk above, and read the cell-level Columbus data from the results text files.

```{r read-columbus-data, message=FALSE}
read_columbus_results <- function(path, glob) {
  dir_ls(path = path,
         recurse = T,
         glob = glob)  %>%
    read_tsv(
      id = "file_name"
    ) %>%
    select(
      screen = ScreenName,
      plate = PlateName,
      well = WellName,
      row = Row,
      column = Column,
      nuc_area = `Nuclei Selected - Nucleus Area [px²]`,
      cyto_area = `Nuclei Selected - Cytoplasm Area [px²]`,
      cell_area = `Nuclei Selected - Cell Area [px²]`,
      nuc_marker_int = `Nuclei Selected - Intensity Nucleus BP600/37 Mean`,
      cyto_marker_int = `Nuclei Selected - Intensity Cytoplasm BP600/37 Mean`,
      ratio_marker_int = `Nuclei Selected - Nuc_Cyto_BP600_Ratio`
    )
}

glob_path <- "*- Nuclei Selected[0].txt"
col_tbl <- read_columbus_results("input", glob_path)

glimpse(col_tbl)
```

Join Columbus data with the plate layout information.

```{r merge-metadata}
cell_tbl <- col_tbl %>%
  mutate(sum_marker_int = nuc_marker_int + cyto_marker_int) %>%
  inner_join(plate_layouts,
             by = c("row", "column")) %>%
  select(screen,
         plate,
         well,
         row,
         column,
         cell_line,
         marker,
         nuc_area:sum_marker_int)

glimpse(cell_tbl)
```

Calculate number of cells and mean per well for all properties.

```{r well-summarise}
well_tbl <- cell_tbl %>%
  group_by(screen,
           well,
           row,
           column,
           cell_line,
           marker) %>%
  summarise(cell_n = n(),
            across(nuc_area:sum_marker_int,
                   list(mean = ~ mean(.x, na.rm = T))))

glimpse(well_tbl)
```

Calculate the mean of the technical replicates for each biological replicate. Now every marker/cell line combination has an n = 3 biological replicates.

```{r bioreps-summarise}
bioreps_tbl <- well_tbl %>%
  group_by(screen,
           cell_line,
           marker) %>%
  summarise(across(cell_n:sum_marker_int_mean,
                    ~ mean(.x, na.rm = T)))

glimpse(bioreps_tbl)
```

### Biological Replicates Level plots for Figure S1H

```{r Fig.S1_H, fig.width=4,fig.height=4.5, echo = FALSE}
bioreps_tbl %>%
  plot_crossbars(property = sum_marker_int_mean,
                 property_legend = "Total Mean Intensity +/- SD",
                 title = "Per Well Total Intensity")
```

### Threshold quantifications

Calculate the mean and standard deviation for the pooled population of controls cells (`WT1`) and on a per biological replicate and on a per marker basis. Set the threshold for quantification of increases or decreases at Mean +/- 1 SD.

```{r calc-thresholds}
thresholds_tbl <- cell_tbl %>% 
  filter(cell_line == "WT") %>%
  group_by(screen, marker) %>%
  summarise(across(nuc_marker_int:sum_marker_int,
                   list(mean_neg = ~ mean(.x, na.rm = T),
                        sd_neg = ~ sd(.x, na.rm = T)))) %>%
  mutate(nuc_marker_plus_thres = nuc_marker_int_mean_neg + 1.5*(nuc_marker_int_sd_neg),
         nuc_marker_minus_thres = nuc_marker_int_mean_neg - 1.5*(nuc_marker_int_sd_neg),
         cyto_marker_plus_thres = cyto_marker_int_mean_neg + 1.5*(cyto_marker_int_sd_neg),
         cyto_marker_minus_thres = cyto_marker_int_mean_neg - 1.5*(cyto_marker_int_sd_neg),
         sum_marker_plus_thres = sum_marker_int_mean_neg + 1.5*(sum_marker_int_sd_neg),
         sum_marker_minus_thres = sum_marker_int_mean_neg - 1.5*(sum_marker_int_sd_neg))

glimpse(thresholds_tbl)
```

```{r}
defects_tbl <- cell_tbl %>%
  left_join(thresholds_tbl, by = c("screen", "marker")) %>%
  group_by(screen, row, column, cell_line, marker) %>%
  summarise(prop_defects_cyto_plus = 100 * mean(cyto_marker_int >= cyto_marker_plus_thres, na.rm = T),
            prop_defects_cyto_minus = 100 * mean(cyto_marker_int <= cyto_marker_minus_thres, na.rm = T),
            prop_defects_nuc_plus = 100 * mean(nuc_marker_int >= nuc_marker_plus_thres, na.rm = T),
            prop_defects_nuc_minus = 100 * mean(nuc_marker_int <= nuc_marker_minus_thres, na.rm = T),
            prop_defects_sum_plus = 100 * mean(sum_marker_int >= sum_marker_plus_thres, na.rm = T),
            prop_defects_sum_minus = 100 * mean(sum_marker_int <= sum_marker_minus_thres, na.rm = T)) %>%
  arrange(screen, marker, cell_line)

glimpse(defects_tbl)
```

```{r bioreps-defects}
bioreps_defects_tbl <- defects_tbl %>%
  group_by(screen, cell_line, marker) %>%
  summarise(across(prop_defects_cyto_plus:prop_defects_sum_minus,
                   list(mean = ~ mean(.x, na.rm = T),
                        sd = ~ sd(.x, na.rm = T))))

glimpse(bioreps_defects_tbl)
```

### Biological Replicates Level plots for Figure S2A

```{r Fig.S2_A, fig.width=4,fig.height=4.5, echo = FALSE}
bioreps_defects_tbl %>%
plot_crossbars(property = prop_defects_sum_plus_mean,
               property_legend = "% of Cells with Plus\nHGPS Total Alterations",
               title = "Total Alterations Plus")
```

### Calculate Dunnett's test for the continuous variables.

Define a custom function to run a Dunnett post-hoc test only on the Mean marker intensity sum (Cyto + Nucleus), using the cell line as the predictor variable, and fixing WT1 as the negative control. The output of the Dunnett's test is then rearranged to a tidy table to make it work with `dplyr`.

```{r}
calc_dunnett <- function(df){
  as.data.frame(as.table(DunnettTest(sum_marker_int_mean ~ cell_line,
                          control = "WT",
                          data = df)$WT)) %>%
    pivot_wider(names_from = Var2, values_from = Freq) %>%
    rename(comparison = Var1)
}
```

Run the custom function on all the data grouped based on the IF marker and save the data to a .csv file.

```{r results='asis'}
dunnett_test <- bioreps_tbl %>%
  group_by(marker) %>%
  group_modify(~ calc_dunnett(.x))

write_csv(dunnett_test, "output/dunnett_results.csv")

knitr::kable(dunnett_test, digits = 3)
```

### Chi-square test for counts/proportion of Cells with defects

Calculate the number of cells with defects and normal on a per well basis. Each treatment has 12 wells (4 technical replicates X 3 biological replicates).

```{r}
defects_counts <- cell_tbl %>%
  left_join(thresholds_tbl, by = c("screen", "marker")) %>%
  group_by(screen, row, column, cell_line, marker) %>%
  summarise(n_cells = n(),
            cyto_plus_def = sum(cyto_marker_int >= cyto_marker_plus_thres, na.rm = T),
            cyto_minus_def = sum(cyto_marker_int <= cyto_marker_minus_thres, na.rm = T),
            nuc_plus_def = sum(nuc_marker_int >= nuc_marker_plus_thres, na.rm = T),
            nuc_minus_def = sum(nuc_marker_int <= nuc_marker_minus_thres, na.rm = T),
            sum_plus_def = sum(sum_marker_int >= sum_marker_plus_thres, na.rm = T),
            sum_minus_def = sum(sum_marker_int <= sum_marker_minus_thres, na.rm = T)) %>%
  mutate(across(cyto_plus_def:sum_minus_def,
                list(norm = ~ n_cells - .x))) %>%
  rename_with( ~ gsub("def_norm", "norm", .x, fixed = TRUE)) %>%
  arrange(screen, marker, cell_line)

defects_counts
```

Summarize the counts by taking the mean of all 12 wells per condition, then pivot the table longer to put in a format that can be handled by xtabs downstream.

```{r}
defects_counts_long <- defects_counts %>%
  select(-n_cells) %>%
  group_by(marker, cell_line) %>%
  summarise(across(cyto_plus_def:sum_minus_norm, # Take the mean of all the wells in all the technical and biological replicates
              ~ mean(.x, na.rm = TRUE))) %>% 
  pivot_longer(cols = cyto_plus_def:sum_minus_norm,
               names_pattern = "(.*_.*)_(.*)",
               names_to = c("type", "quality"),
               values_to = "count")

defects_counts_long
```

Define a function that calculate a contingency table of counts based on the cell line and the cell class (normal/defects). The table is then used to calculate the chi-square test to determine whether any of the 6 cell lines is different from the others in terms of proportion of defects.

```{r}
calc_chi <- function(df){
    xtabs_tbl <- xtabs(count ~ cell_line + quality, data = df)
    broom::tidy(chisq.test(xtabs_tbl))
}
```

Apply the function on a per IF marker and on a per defect category to calculate the p-values on a per IF marker and defect type basis.

```{r}
chi_square_test <- defects_counts_long %>%
  group_by(marker, type) %>%
  group_modify(~ calc_chi(.x))

write_csv(chi_square_test, "output/chi_square_results.csv")

knitr::kable(chi_square_test, digits = 3)
```

Document the information about the analysis session

```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```
