---
title: "Figure 4E: TETON Cells / GRP78"
author: "Sandra Vidak"
date: "November 16th 2022"
output: github_document
---

```{r load-packages}
library(ggplot2)
library(ggthemes)
library(curl)
```

```{r set-knitr-options, include=FALSE}
knitr::opts_chunk$set(
  fig.path = 'output/',
  message = FALSE,
  warning = FALSE
  )
```

### Download the data if needed

Download and unzip the Columbus results of the experiments from Figshare if they have not been already downloaded.

```{r download-data}
if(!dir.exists("input")) {
  URL <- "https://figshare.com/ndownloader/files/38158380"
  curl_download(URL, "input.zip")
  unzip("input.zip")
}
```

### Read Data for Fig 4E

Import and filter data and calculate sum and mean of the GRP78 peripheral recruitment for each biological replicate in TetON fibroblasts.

```{r}
GRP78_1 <- read.csv(file="input/GRP78ring1.csv") 

GRP78_1_filtered <- GRP78_1 [ c(seq(1, nrow(GRP78_1),1)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_1_Induced_filtered <- GRP78_1 [ c(seq(4, nrow(GRP78_1),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_1_siSUN1_filtered <- GRP78_1 [ c(seq(5, nrow(GRP78_1),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_1_siSUN2_filtered <- GRP78_1 [ c(seq(6, nrow(GRP78_1),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_1_U_filtered_rowsum <- rowSums(GRP78_1_filtered[,1:2])

GRP78_1_Induced_filtered_rowsum <- rowSums(GRP78_1_Induced_filtered[,1:2])

GRP78_1_siSUN1_filtered_rowsum <- rowSums(GRP78_1_siSUN1_filtered[,1:2])

GRP78_1_siSUN2_filtered_rowsum <- rowSums(GRP78_1_siSUN2_filtered[,1:2])

Mean_Uninduced_GRP78_1 <- mean(GRP78_1_U_filtered_rowsum[1:3])

Mean_Induced_siCTRL_GRP78_1 <- mean(GRP78_1_Induced_filtered_rowsum[1:3])

Mean_Induced_siSUN1_GRP78_1 <- mean(GRP78_1_siSUN1_filtered_rowsum[1:3])

Mean_Induced_siSUN2_GRP78_1 <- mean(GRP78_1_siSUN2_filtered_rowsum[1:3])


```

```{r}
GRP78_2 <- read.csv(file="input/GRP78ring2.csv") 

GRP78_2_filtered <- GRP78_2[ c(seq(1, nrow(GRP78_2),1)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_2_Induced_filtered <- GRP78_2 [ c(seq(4, nrow(GRP78_2),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_2_siSUN1_filtered <- GRP78_2 [ c(seq(5, nrow(GRP78_2),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_2_siSUN2_filtered <- GRP78_2 [ c(seq(6, nrow(GRP78_2),4)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_2_U_filtered_rowsum <- rowSums(GRP78_2_filtered[,1:2])

GRP78_2_Induced_filtered_rowsum <- rowSums(GRP78_2_Induced_filtered[,1:2])

GRP78_2_siSUN1_filtered_rowsum <- rowSums(GRP78_2_siSUN1_filtered[,1:2])

GRP78_2_siSUN2_filtered_rowsum <- rowSums(GRP78_2_siSUN2_filtered[,1:2])

Mean_Uninduced_GRP78_2 <- mean(GRP78_2_U_filtered_rowsum[1:3])

Mean_Induced_siCTRL_GRP78_2 <- mean(GRP78_2_Induced_filtered_rowsum[1:3])

Mean_Induced_siSUN1_GRP78_2 <- mean(GRP78_2_siSUN1_filtered_rowsum[1:3])

Mean_Induced_siSUN2_GRP78_2 <- mean(GRP78_2_siSUN2_filtered_rowsum[1:3])
```

```{r}

GRP78_3 <- read.csv(file="input/GRP78ring3.csv") 
GRP78_3_filtered <- GRP78_3 [ c(seq(1, nrow(GRP78_3),1)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_3_Induced_filtered <- GRP78_3 [ c(seq(4, nrow(GRP78_3),3)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_3_siSUN1_filtered <- GRP78_3 [ c(seq(5, nrow(GRP78_3),3)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_3_siSUN2_filtered <- GRP78_3 [ c(seq(6, nrow(GRP78_3),3)), c("Intensity.Nucleus.3", "Intensity.Nucleus.4")]

GRP78_3_U_filtered_rowsum <- rowSums(GRP78_3_filtered[,1:2])

GRP78_3_Induced_filtered_rowsum <- rowSums(GRP78_3_Induced_filtered[,1:2])

GRP78_3_siSUN1_filtered_rowsum <- rowSums(GRP78_3_siSUN1_filtered[,1:2])

GRP78_3_siSUN2_filtered_rowsum <- rowSums(GRP78_3_siSUN2_filtered[,1:2])

Mean_Uninduced_GRP78_3 <- mean(GRP78_3_U_filtered_rowsum[1:3])

Mean_Induced_siCTRL_GRP78_3 <- mean(GRP78_3_Induced_filtered_rowsum[1:3])

Mean_Induced_siSUN1_GRP78_3 <- mean(GRP78_3_siSUN1_filtered_rowsum[1:3])

Mean_Induced_siSUN2_GRP78_3 <- mean(GRP78_3_siSUN2_filtered_rowsum[1:3])
```

```{r}
GRP78_Uninduced <- c(Mean_Uninduced_GRP78_1, Mean_Uninduced_GRP78_2, Mean_Uninduced_GRP78_3)

GRP78_Induced_siCTRL <- c(Mean_Induced_siCTRL_GRP78_1, Mean_Induced_siCTRL_GRP78_2, Mean_Induced_siCTRL_GRP78_3)

GRP78_Induced_siSUN1 <- c(Mean_Induced_siSUN1_GRP78_1, Mean_Induced_siSUN1_GRP78_2, Mean_Induced_siSUN1_GRP78_3)

GRP78_Induced_siSUN2 <- c(Mean_Induced_siSUN2_GRP78_1, Mean_Induced_siSUN2_GRP78_2, Mean_Induced_siSUN2_GRP78_3)


GRP78_df <- data.frame (GRP78_Uninduced,GRP78_Induced_siCTRL,GRP78_Induced_siSUN1, GRP78_Induced_siSUN2 )
rownames(GRP78_df) <- c("Biological replicate1", "Biological replicate2", "Biological replicate3")
```

Calculate mean and SD for 3 different biological replicates in every condition

```{r}
Mean_GRP78_levels <- apply (GRP78_df,2,mean)

SD_GRP78_levels <- apply (GRP78_df,2,sd)

Mean_GRP78_levels2 <- as.data.frame(Mean_GRP78_levels)

SD_GRP78_levels2 <- as.data.frame(SD_GRP78_levels)
Condition <- rep(c("GFP-progerin OFF","GFP-progerin ON", "siSUN1", "siSUN2"), each=1)
GRP78_plot <- data.frame(Mean_GRP78_levels2,SD_GRP78_levels2, Condition )
```

### Biological Replicates Level plot for Fig.4E

```{r Fig_3C, echo=FALSE}
ggplot(GRP78_plot, aes(x = Condition, y = Mean_GRP78_levels, 
                       ymin = Mean_GRP78_levels-SD_GRP78_levels, 
                       ymax = Mean_GRP78_levels+SD_GRP78_levels)) + 
  geom_crossbar()+ ylab("Mean Peripheral Intensity +/-SD [a.u.]") + 
  ggtitle("Per Well Total Intensity")+ 
  scale_y_continuous(expand = c(0, 0), limits = c(0,25000))
```

Document the information about the analysis session

```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```
